Negative and Fractional Types

### 2012-06-27 rational_ext.tex
dgm
_

%%%%%%%%%%%%%%%
\subsection{Constructions}

@@

\dgm{if-c1-c2}

@@

\roshan{Maybe replace the annihilation example with union and
  difference.}

@@

\roshan{This probably needs rigorous proof.}

\roshan{Should we show completeness -- i.e. that every relation is
  expressible? We can. But should we?}

@@

%%%%%%%%%
\subsection{Categorical Constructions}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{SAT Solver }
\label{sec:prog}
\label{sec:sat-solver}

@@

Any boolean expression {{f : bool^n -> bool}} can be compiled into the
isomorphism {{iso_f : bool^h*bool^n<->bool^g*bool}} where the extra bits
{{bool^h}} and {{bool^g}} are considered as heap and garbage. Constructing
such an isomorphism has been detailed
before~\cite{Toffoli:1980,infeffects}. The important relation to note is that
applying {{iso_f}} to some special heap values and an input \textit{bs}
produces some bits that can be ignored and the same output that {{f}} would
have produced on {{bs}}. We can ensure that the heap has the appropriate
initial values by checking the heap and negating a second control wire, if
the values do not match, i.e., the dotted part in the diagram below.

@@

When the solver is fed inputs initialized to {{true}}, it clones only
those inputs to {{sat_f}} that satisfy {{f}} and the heap
constraints. In the case of unique-SAT the solver will produce exactly
0 or 1 solutions. In the case of general SAT, the solver will produce
solutions as determined by the semantics of the top-level interaction
(see discussion in Sec. \ref{sec:rat}).

>>>>

%%%%%%%%%%%%%%%
\subsection{Constructions}
\label{sec:pi-constructions}

@@

% \dgm{if-c1-c2}

@@

%% \roshan{Maybe replace the annihilation example with union and
%%   difference.}

@@

% \roshan{This probably needs rigorous proof.}

\paragraph*{Union.}
The union of the two relations {{c1:b1<->b2}} and {{c2:b1<->b2}} is
expressed by {{trace* if_{c1,c2} :b1<->b2}} (see Sec.
\ref{sec:pi-constructions} for {{if_{c1,c2} }} and
Sec. \ref{sec:frac-constructions} for {{trace*}}). Intersection can be
expressed by ``controlled-annihilation'' detailed in
Sec. \ref{sec:sat-solver}.

%% \roshan{Should we show completeness -- i.e. that every relation is
%%   expressible? We can. But should we?}

@@

%%%%%%%%%
\subsection{Categorical Constructions}
\label{sec:frac-constructions}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{SAT Solver }
\label{sec:sat-solver}

@@

Any boolean expression {{f : bool^n -> bool}} can be compiled into the
isomorphism {{iso_f : bool^h*bool^n<->bool^g*bool}} where the extra
bits {{bool^h}} and {{bool^g}} are considered as heap and
garbage. Constructing such an isomorphism has been detailed
before~\cite{Toffoli:1980,infeffects}. The important relation to note
is that applying {{iso_f}} to some special heap values and an input
\textit{bs} produces some bits that can be ignored and the same output
that {{f}} would have produced on {{bs}}. We can ensure that the heap
has the appropriate initial values by checking the heap and negating a
second control wire, if the values do not match using, i.e., the
dotted part in the diagram below. This is achieved by first applying
{{not}} to the control wire and then testing that all the heap values
are true using {{cnot^n}}, undoing the {{not}} only if they are.

@@

When the solver is fed inputs initialized to {{true}}, it clones only
those inputs to {{sat_f}} that satisfy {{f}} and the heap
constraints. In the case of unique-SAT the solver will produce exactly
0 or 1 solutions. In the case of general SAT, the solver will produce
all satisfying solution.
